Spatiotemporal models of species biomass with time-varying DO

### 2019-09-06 analysis/VOCC/1-biomass-do-models-fixed-both.Rmd
add species; allow to run for those not split by maturity

# # Species run so far...
# species <- "Arrowtooth Flounder"
# species <- "Pacific Cod"
# species <- "Sablefish"
# species <- "Silvergray Rockfish"
# species <- "Lingcod"
# species <- "North Pacific Spiny Dogfish" # note: using all data for maturity thresholds
 species <- "Quillback Rockfish"
# species <- "Pacific Ocean Perch"
# species <- "Yelloweye Rockfish"
```

@@

  # scale predictors before filtering to ensure mean and SD are global
  data <- data %>% mutate(raw_depth = depth_bath, depth = log(raw_depth), temp = temperature_c) 
  do_data <- scale_predictors(data, predictors = c(quo(depth), quo(temp), quo(do_mlpl)))
       # c(quo(log_depth), quo(mixed), quo(muddy), quo(sandy), quo(rocky), quo(any_rock)))
  data <- do_data %>% mutate(depth = raw_depth) %>% #filter(year != 2016) %>%
    filter(ssid %in% model_ssid) %>% 
    filter(!is.na(do_mlpl)) %>% filter(!is.na(depth_scaled)) %>% filter(!is.na(temp))%>% 
    select(X, Y, X10, Y10, adult_density, imm_density, depth_scaled, depth_scaled2, depth_mean, depth_sd, do_mlpl_scaled, do_mlpl_scaled2,  do_mlpl_mean, do_mlpl_sd, temp_scaled, temp_scaled2, temp_mean, temp_sd, trawled, any_rock, muddy, sandy, year, ssid, fishing_event_id, depth, do_mlpl) %>% filter(!is.na(depth_scaled)) 
```

>>>>

# # Species run so far...
# species <- "Arrowtooth Flounder"
# species <- "Petrale Sole"
# species <- "English Sole"
# species <- "Dover Sole" # maturity data error for WCHG
# species <- "Southern Rock Sole"
# species <- "Flathead Sole"

# species <- "Walleye Pollock"
# species <- "Pacific Cod"
# species <- "Pacific Ocean Perch"

# species <- "Silvergray Rockfish"
# species <- "Quillback Rockfish"
# species <- "Yelloweye Rockfish"
# species <- "Bocaccio"
# species <- "Sharpchin Rockfish"
# species <- "Splitnose Rockfish"
# species <- "Canary Rockfish"
# species <- "Rougheye/Blackspotted Rockfish Complex"
# species <- "Redbanded Rockfish"
# species <- "Greenstriped Rockfish"

# species <- "Longspine Thornyhead"
# species <- "Shortspine Thornyhead",
# species <- "Sablefish"
# species <- "Lingcod"

# species <- "North Pacific Spiny Dogfish" # note: using all data for maturity thresholds
# species <- "Longnose Skate"
species <- "Spotted Ratfish"

```

@@

  # scale predictors before filtering to ensure mean and SD are global
  data <- data %>% mutate(raw_depth = depth_bath, depth = log(raw_depth), temp = temperature_c) 
  do_data <- scale_predictors(data, predictors = c(quo(depth), quo(temp), quo(do_mlpl))) 
       # c(quo(log_depth), quo(mixed), quo(muddy), quo(sandy), quo(rocky), quo(any_rock)))
  data <- do_data %>% mutate(depth = raw_depth) %>% #filter(year != 2016) %>%
    filter(ssid %in% model_ssid) %>% 
    filter(!is.na(depth_scaled)) %>% filter(!is.na(do_mlpl)) %>% filter(!is.na(temp))

if (any(names(data) == "adult_density")) { 
  data <- data %>% select(X, Y, X10, Y10,
      adult_density, imm_density,
      depth_scaled, depth_scaled2, depth_mean, depth_sd, 
      do_mlpl_scaled, do_mlpl_scaled2,  do_mlpl_mean, do_mlpl_sd, 
      temp_scaled, temp_scaled2, temp_mean, temp_sd, 
      trawled, any_rock, muddy, sandy, year, ssid, fishing_event_id, 
      depth, do_mlpl) 
 } else {
    data <- data %>% select(X, Y, X10, Y10,
      density,
      depth_scaled, depth_scaled2, depth_mean, depth_sd, 
      do_mlpl_scaled, do_mlpl_scaled2,  do_mlpl_mean, do_mlpl_sd, 
      temp_scaled, temp_scaled2, temp_mean, temp_sd, 
      trawled, any_rock, muddy, sandy, year, ssid, fishing_event_id, 
      depth, do_mlpl) 
}
```
